Domain-agnostic Outlier Ranking Algorithms (DORA)---A Configurable Pipeline for Facilitating Outlier Detection in Scientific Datasets

### 2021-09-18 publications/iaai21/dora_outlier_detection_iaai.tex
Add discussion of overall algorithm performance. #42

\paragraph{Algorithm performance.} \todo{Discuss overall results from
 experiments and that we left hyperparameter tuning and extensive
 evaluation for future work.}

>>>>

\paragraph{Algorithm performance.} There was no one algorithm that 
 had the best performance across all four datasets. PCA had
the best performance for the astrophysics and F-MNIST datasets, 
while negative sampling and isolation forest was best for
the Earth science and planetary datasets respectively. This illustrates
the importance of including a diverse set of algorithms and tools for
easily inter-comparing them in DORA, since the best
algorithm will vary for different datasets. The purpose of this study
was to demonstrate how DORA could be used to facilitate 
outlier detection experiments and compare results across datasets from 
different domains. Thus we chose hyperparameters based on common 
practice and sense and left hyperparameter tuning, which would likely 
improve results for each dataset but would require
creation of additional validation sets, for future work.
